Instructions for ACL 2020 Proceedings

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
add model section

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}

@@

\section{Model} % Bill
%  - DAR model -> utt encoder, RNN sequence tagger
%  - BERT encoder (12 heads, uncased,...)
%  - baseline encoder

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{amsmath}

@@

\section{Model} % Bill

Our DAR model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag (figure \ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
The RNN takes the encoded utterance as input at each time step
Its hidden state is passed to a simple linear classification layer over dilague act tags.
Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.

\begin{figure*}
  \include{model}
  \caption{DAR model architecture}
  \label{fig:model-architecture}
\end{figure*}
%  - DAR model -> utt encoder, RNN sequence tagger
%  - BERT encoder (12 heads, uncased,...)
%  - baseline encoder
